Back to ``Normal'' for the Disintegrating Planet Candidate KIC 12557548 b

### 2018-05-03 ms.tex
some more details on spectroscopy and added a row to the parameters table.

\begin{deluxetable*}{lcrrr}
\tablecaption{Observational estimates of the stellar parameters of KIC~12557548 from \citet{vanlieshout2016kic1255}}
\tablewidth{0pt}
\tablehead{
\colhead{Reference} &
\colhead{$ T_{eff,*} $} &
\colhead{$\log(g)$} &
\colhead{Evolutionary Status} &
\colhead{Method} \\
 & (K) & $\log$(cm s$^{-2}$) & & \\
 }
\startdata
  \citet{brown2011kic} & 4400 $\pm$ 200   & 4.6 $\pm$ 0.5    & main-sequence star & photometry \\
  \citet{rappaport}       & 4300 $\pm$ 250    &                            & main-sequence star & low-resolution spectroscopy \\
  \citet{kawahara2013starspots} & 4950 $\pm$ 70 & 3.9 $\pm$ 0.2 & sub-giant          & high-resolution spectroscopy \\
  \citet{huber2014kicprop} & 4550$^{+140}_{-131} $ & 4.622$^{+0.043}_{-0.036} $& main-sequence star & photometry \\
  This work - Specmatch	& 4500 $\pm$110 	& 4.63 $\pm$ 0.1 & main-sequence star & high-resolution spectroscopy\\
  This work - BOSZ		& 4500	& 4.5		& main-sequence star & high-resolution spectroscopy\\
\enddata
\tablenotetext{}{While most of the photometric results show a surface gravity of a main sequence star, the high resolution analysis from \citet{kawahara2013starspots} indicates a gravity consistent with a sub-giant star.}\label{tab:stellObsParams}
\end{deluxetable*}

The host star \shStar\ has been characterized by both photometry and spectroscopy.
Table \ref{tab:stellObsParams} shows the summary of observations and analyses compiled in \citet{vanlieshout2016kic1255} for the stellar properties, re-produced here.
In the photometric analysis and low resolution spectroscopy, the spectra are consistent with a 4500 K main sequence K-type star.
High resolution spectra, however, indicate a higher temperature 4900 K lower log(g) sub-giant star \citep{kawahara2013starspots}.
\citet{vanlieshout2016kic1255} analyzed the light curve with a dust model to put constraints on the semi-major axis, which in turn constrains the density of the star when combined with Kepler's third law \citep{seager2003uniqueSolution}.
\citet{vanlieshout2016kic1255} find that the stellar density is only consistent with a main-sequence star with log(g) $\gtrsim 4.4 \log($cm s$^{-2})$.
They suggest an intriguing possibility that the high resolution spectrum of \shStar\ has contamination from dusty debris from the planet and thus appears as a sub-giant star.
If true, high resolution spectra would be valuable tool to study the composition and dynamics of the material escaping \sha.

@@

We decided to re-visit the stellar parameters by examining the spectra taken with the High Definition Spectrograph (HDS) spectrograph on the Subaru telescope \citep{noguchi2002hds}.
There is one set of data taken on 2013-06-22 discussed in \citet{kawahara2013starspots}.
Additionally, there is one set of observations from 2015-08-28 that was taken to understand the kinematics of the system.
Both of these observations happened after the reaction wheel failure on 2015-05-11\footnote{https://www.nasa.gov/mission\_pages/kepler/news/keplerm-20130521.html}, so no simultaneous Kepler photometry was available with the high dispersion spectroscopy.

@@

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.49\textwidth]{images/kepler/amplitude_periodogram.pdf}
\caption{Periodogram of the amplitude time series shown in Figure \ref{fig:PCAamp}
Bootstrap error estimates for the 2$\sigma$ and 3$\sigma$ confidence intervals are shown.
The peak at 0.654 days is the orbital period.
The peaks at 153 and 750 days are likely caused by the longer intervals of low disintegration activity.
The 22.9 day peak is consistent with the \citet{kawahara2013starspots} peak that is co-incident with the stellar rotation period.}\label{fig:PCAamp}
\end{centering}
\end{figure*}

>>>>

\begin{deluxetable*}{lcrrr}
\tablecaption{Observational estimates of the stellar parameters of KIC~12557548 from \citet{vanlieshout2016kic1255}}
\tablewidth{0pt}
\tablehead{
\colhead{Reference} &
\colhead{$ T_{eff,*} $} &
\colhead{$\log(g)$} &
\colhead{Evolutionary Status} &
\colhead{Method} \\
 & (K) & $\log$(cm s$^{-2}$) & & \\
 }
\startdata
  \citet{brown2011kic} & 4400 $\pm$ 200   & 4.6 $\pm$ 0.5    & main-sequence star & photometry \\
  \citet{rappaport}       & 4300 $\pm$ 250    &                            & main-sequence star & low-resolution spectroscopy \\
  \citet{kawahara2013starspots} & 4950 $\pm$ 70 & 3.9 $\pm$ 0.2 & sub-giant          & high-resolution spectroscopy \\
  \citet{huber2014kicprop} & 4550$^{+140}_{-131} $ & 4.622$^{+0.043}_{-0.036} $& main-sequence star & photometry \\
  \citet{morton2016falsePos} & 4677 		& 4.61		& main-sequence star	& photometry \\
  This work - Specmatch	& 4500 $\pm$110 	& 4.63 $\pm$ 0.1 & main-sequence star & high-resolution spectroscopy\\
  This work - BOSZ		& 4500	& 4.5		& main-sequence star & high-resolution spectroscopy\\
\enddata
\tablenotetext{}{While most of the photometric results show a surface gravity of a main sequence star, the high resolution analysis from \citet{kawahara2013starspots} indicates a gravity consistent with a sub-giant star.}\label{tab:stellObsParams}
\end{deluxetable*}

The host star \shStar\ has been characterized by both photometry and spectroscopy.
Table \ref{tab:stellObsParams} shows the summary of observations and analyses compiled in \citet{vanlieshout2016kic1255} for the stellar properties, re-produced here with additional results added from .
In the photometric analysis and low resolution spectroscopy, the spectra are consistent with a 4500 K main sequence K-type star.
High resolution spectra, however, indicate a higher temperature 4900 K lower log(g) sub-giant star \citep{kawahara2013starspots}.
\citet{vanlieshout2016kic1255} analyzed the light curve with a dust model to put constraints on the semi-major axis, which in turn constrains the density of the star when combined with Kepler's third law \citep{seager2003uniqueSolution}.
\citet{vanlieshout2016kic1255} find that the stellar density is only consistent with a main-sequence star with log(g) $\gtrsim 4.4 \log($cm s$^{-2})$.
They suggest an intriguing possibility that the high resolution spectrum of \shStar\ has contamination from dusty debris from the planet and thus appears as a sub-giant star.
If true, high resolution spectra would be valuable tool to study the composition and dynamics of the material escaping \sha.

@@

We decided to re-visit the stellar parameters by examining the spectra taken with the High Definition Spectrograph (HDS) spectrograph on the Subaru telescope \citep{noguchi2002hds}.
There is one set of data taken on 2013-06-22 (UT) discussed in \citet{kawahara2013starspots}, including 4 exposures each 2700 seconds in duration.
Additionally, there are two set of observations from 2015-08-28 (UT) and 2015-08-29 (UT) that were taken to understand the kinematics of the system \citep{masuda2018rvKIC1255}, with exposure durations of 2400 seconds each.
The second set of observations happened after the reaction wheel failure on 2015-05-11\footnote{https://www.nasa.gov/mission\_pages/kepler/news/keplerm-20130521.html} that ended photometry of the main Kepler field, so no simultaneous Kepler photometry was available with the high dispersion spectroscopy.

@@

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.49\textwidth]{images/kepler/amplitude_periodogram.pdf}
\caption{Periodogram of the amplitude time series shown in Figure \ref{fig:PCAamp}
Bootstrap error estimates for the 2$\sigma$ and 3$\sigma$ confidence intervals are shown.
The peak at 0.654 days is the orbital period.
The peaks at 153 and 750 days are likely caused by the longer intervals of low disintegration activity.
The 22.9 day peak is consistent with the \citet{kawahara2013starspots} peak that is co-incident with the stellar rotation period.}\label{fig:ampPeriodogram}
\end{centering}
\end{figure*}
